A Large-scale Study of Polymorphism in R

### 2019-03-24 paper/main.tex
more examples, with some descriptions. more to come

\lstset{ %
  columns=flexible,
  captionpos=b,
  frame=single,
  framerule=0pt,
  framexleftmargin=-1mm,
  framexrightmargin=-1mm,
  tabsize=2,
  belowskip=0pt,
  basicstyle=\small\ttfamily,
  backgroundcolor=\color{LightGray},
  emphstyle=\sffamily,
  keywordstyle=\bfseries,
  commentstyle=\color{Gray}\em,
  stringstyle=\color{Gray}
}

@@

%
\section{Results}\label{sec:results}

\AT{Collection of examples of polymorphism...}

\begin{figure}[!hb]{\small\begin{lstlisting}[style=R]
# w here is weights
frac.ranks <- function(x, w=NULL) {
  if (is.null(w)) w <- rep(1, length(x)) # if no weights passed, take all weights = 1
  ...
\end{lstlisting}}\caption{Example of optional argument (from {\tt acid} package).}\label{fig:optnull}\end{figure}

@@

\begin{figure}[!hb]{\small\begin{lstlisting}[style=R]
nret.translator <- function(dat, spss="out", ...){
  ...
  if(identical(spss, "out")) {
    if(!is.vector(dat)) {
        stop(simpleError("If 'corr=TRUE', 'dat' must be a vector!"))
      }
    ...
  } else {
    ...
    # here, dat is data.frame
    items.idx <- items.idx[order(names(dat[, items.idx]))]
  }

\end{lstlisting}}\caption{Example of data.frame/vector/double argument (from {\tt klausR} package).}\label{fig:charclos}\end{figure}

>>>>

\lstset{ %
  columns=flexible,
  captionpos=b,
  frame=single,
  framerule=0pt,
  framexleftmargin=-1mm,
  framexrightmargin=-1mm,
  tabsize=2,
  belowskip=0pt,
  basicstyle=\small\ttfamily,
  backgroundcolor=\color{LightGray},
  emphstyle=\sffamily,
  keywordstyle=\bfseries,
  commentstyle=\color{Gray}\em,
  stringstyle=\color{Gray},
  numbers=left
}

@@

%
%
%
%
%
%
\section{Examples of Polymorphism}
\label{sec:polyex}

Figure~\ref{fig:optnull} shows an example of a function with an optional argument.
In the function, {\tt x} is a sorted vector of income values, and {\tt w} is a vector of weights, optionally NULL.
The function computes fractional ranks required for the computation of some coefficient implemented by the package.
We see that if {\tt w} is NULL, then default unit weights are generated.

\begin{figure}[!hb]{\small\begin{lstlisting}[style=R]
frac.ranks <- function(x, w=NULL) {
  if (is.null(w)) w <- rep(1, length(x)) # if no weights passed, take all weights = 1
  ...
\end{lstlisting}}\caption{Example of optional argument (from {\tt acid} package).}\label{fig:optnull}\end{figure}

Figure~\ref{fig:listvec} shows an example of a function with list and vector polymorphism.
The function takes a list or vector {\tt point} and a data frame {\tt polyg} representing a polygon.
In it, we see that {\tt point} can be either a list or a vector, and the function code casts the argument to a double vector.

@@

\AT{I'll explain this better, maybe?}
In Figure~\ref{fig:dfdbl}, we see a function that, among other things, takes in some data ({\tt dat}) and a character string ({\tt spss}) specifying either {\tt "in"} or {\tt "out"}.
Now, depending on the value of {\tt spss}, {\tt dat} will either be a data frame or a vector of doubles.
\AT{This ties in to the (arg, retv) coupling, which we will have data on soon.}

\begin{figure}[!hb]{\small\begin{lstlisting}[style=R]
nret.translator <- function(dat, spss="out", ...){
  ...
  if(identical(spss, "out")) {
    if(!is.vector(dat)) {
        stop(simpleError("...'dat' must be a vector!"))
      }
    ...
  } else {
    ...
    # here, dat is data.frame
    items.idx <- items.idx[order(names(dat[, items.idx]))]
  }
\end{lstlisting}}\caption{Example of a data.frame/(vector/double) argument (from {\tt klausR} package).}\label{fig:dfdbl}\end{figure}

In Figure~\ref{fig:chardbl}, we see a function which takes in a list ({\tt network}), a vector of indices of that list ({\tt fixIndices}), and a vector of values ({\tt values}).
The locations specified by {\tt fixIndicies} in {\tt network} are updated with {\tt values}.
Here, {\tt fixIndicies} has been observed to be either a character or double vector:
In R, list indices are typically doubles, but can be characters (if the list or vector being indexed has a {\tt names} attribute).

\begin{figure}[!hb]{\small\begin{lstlisting}[style=R]
fixGenes <- function (network, fixIndices, values)  {
  ...
  network$fixed[fixIndices] <- as.integer(values)
  ...
}
\end{lstlisting}}\caption{Example of character/double argument (from {\tt BoolNet} package).}\label{fig:chardbl}\end{figure}

%
%
%
%
%
%
\section{Results}\label{sec:results}
